The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-27 paper.Rmd
grammar fix

This section explores the practical application of the Gillespie Algorithm by simulating two molecular systems. The first simulation, [Photodimerization Simulation](#sec-Photodimerization), models the photodimerization of thymine, a molecular reaction relevant to DNA damage caused by ultraviolet (UV) radiation. The second simulation, [Radioactive Decay Simulation](#sec-Decay), examines the stochastic decay of radioactive isotopes, a fundamental process in nuclear physics. Both simulations references the `GillespieSSA` package (@GillespieSSA), a R implementation of the Gillespie Algorithm that facilitates the generation of statistically accurate trajectories for molecular reaction systems. By consulting this package, we can simulate complex stochastic processes and explore the dynamics of these reaction systems.

>>>>

This section explores the practical application of the Gillespie Algorithm by simulating two molecular systems. The first simulation, [Photodimerization Simulation](#sec-Photodimerization), models the photodimerization of thymine, a molecular reaction relevant to DNA damage caused by ultraviolet (UV) radiation. The second simulation, [Radioactive Decay Simulation](#sec-Decay), examines the stochastic decay of radioactive isotopes, a fundamental process in nuclear physics. Both simulations reference the `GillespieSSA` package (@GillespieSSA), a R implementation of the Gillespie Algorithm that facilitates the generation of statistically accurate trajectories for molecular reaction systems. By consulting this package, we can simulate complex stochastic processes and explore the dynamics of these reaction systems.
